---
title: "Eating Out"
author: "Laizha Grajeda De Leon"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

Based on the frequency table above, which shows the volume of people who do not eat out for each racial group, we can see that about 950 white people eat out while 200 do not. Meanwhile, about 200 black people eat out while 100 do not. For the other racial groups, about 100 people while about 50 do not. Putting this into percentages, 80% of white people eat out and 20% do not. Meanwhile, black and others have about the same percentages with 70% of them eat out and 30% do not. 



